Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-04-20 paper/paper.tex
Merge Mikhail's changes

@@

\begin{abstract}
The linear variation is a topological characteristic of the function of two variables.
The problem of linear variation computing can be reduced to the problem of counting connected components in a binary image with eight-connected connectivity.
%The new hybrid method for the problem is presented.
%The method is essentially a modification of a two-scan algorithm for labeling
%that groups the pixels into $2 \times 2$ cells.
This is usually done through connected components labeling, and many approaches for that are known.
This paper presents an efficient way to convert the initial binary image with 8-connectivity into a condensed (non-binary) image with new connectivity that is 2 times smaller in each dimension than the initial image.
Most approaches for connected components labeling are still valid for the new image.
As time and memory consumptions of conventional approaches usually depend linearly on the number of pixels,
running them on the condensed image can be up to 4 times more efficient than running on the initial image.
The method is essentially a modification of some known raster algorithms for labeling that groups pixels into $2 \times 2$ cells.
A performance benchmark of the proposed  method applied to some approaches on noise images is provided.

@@

In image restoration it is often necessary to consider the following problem.
How to restore an original undistorted image $v$, if it is known an observed
image $u_0$ and the relation between $u_0$ and $v$:
\begin{equation}
  u_0=v+n,
  \label{eq:imageRelation}
\end{equation}
where $n$ is a noise?
A common way for solving the problems \eqref{eq:imageRelation} is to use the
variational functionals.
One of the most widely used approaches is total variation
regularization\cite{mak1}.
Let $J(u)$ be the following functional:
\begin{equation}
  J(u) = \frac12 \norm{u - u_0}^2 + \lambda TV(u),
  \label{eq:jFunctional}
\end{equation}
where $\norm{\cdot}$ is the $L_2$ norm and all function we consider belong to the class
$BV(\Omega)$, i.\,e. the class of bounded variation on the set $\Omega$ functions.
%
The expression $\frac12 \norm{n-n_0}^2$ is called a fidelity term and
$\lambda TV(u)$ is called a regularization term and $\lambda$ is regularization
parameter.

@@

@@

This problem is equivalent to the problem of counting the number of connected
components (CC) in a binary image with 8-connectivity.
This is usually done through CC labeling, and many approaches for that are
known\cite{hechao}.

@@

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \node[cell] at (0.5, 0.5) {};
    \foreach \x/\y [count=\i from 0] in {0/1,1/1,0/0,1/0} {
      \node[whitebox] at (\x,\y) {\i};
    }
  \end{tikzpicture}
  \caption{Cell pixels enumeration}
  \label{fig:pixelsEnumeration}
\end{figure}

@@

\texten{
Note that this algorithm outputs not the matrix of final labels, but only the number
of CC.
This is the place in which it differs from some common two-pass approaches for CC % TODO references
labeling, as it is an algorithm not for labeling, but just for counting CC.
The latter is exactly what is needed for the aforementioned linear variation problem.
}\textru{
Отметим, что этот алгоритм выдаёт не матрицу финальных меток, а только
количество компонент связности.
Именно в этом месте он отличается от некоторых известных подходов к CC labeling.
Для текущей задачи нам нужно именно считать компоненты связности.
}

@@

% \section{Summary and future work}

@@

\bibitem {mak1}
Rudin, L., Osher, S., Fatemi, E.:
Nonlinear total variation based noised removal algorithms.
Phys. D. 60, 259-268 (1992)

% \bibitem {mak2}
% Kronrod, A.:
% On functions of two variables.
% Uspehi Mat. Nauk 5, 1(35), 24-134(1950)

>>>>

\usepackage{verbatim}

@@

\begin{abstract}
The linear variation is a topological characteristic of the function of two
variables. The problem of linear variation computing can be reduced to the
problem of counting connected components in a binary image with eight-connected
connectivity.
%The new hybrid method for the problem is presented.
%The method is essentially a modification of a two-scan algorithm for labeling
%that groups the pixels into $2 \times 2$ cells.
%This is usually done through connected components labeling, and many approaches
%for that are known. This paper presents an efficient way to convert the initial
%binary image with 8-connectivity into a condensed %(non-binary) image with new
%connectivity that is 2 times smaller in each dimension than the initial image.
%Most approaches for connected components labeling are still valid for the new
%image. As time and memory consumptions of conventional approaches usually
%depend linearly on the number of pixels, running them on the condensed image
%can be up to 4 times more efficient than running on the initial image.
The method is essentially a modification of some known raster algorithms for
labeling that groups pixels into $2 \times 2$ cells. A performance benchmark of
the proposed  method applied to some approaches on noise images is provided.

@@

\begin{comment}
In image restoration it is often necessary to consider the following problem.
How to restore an original undistorted image $v$, if it is known an observed
image $u_0$ and the relation between $u_0$ and $v$:
\begin{equation}
  u_0=v+n,
  \label{eq:imageRelation}
\end{equation}
where $n$ is a noise?
A common way for solving the problems \eqref{eq:imageRelation} is to use the
variational functionals.
One of the most widely used approaches is total variation
regularization\cite{mak1}.
Let $J(u)$ be the following functional:
\begin{equation}
  J(u) = \frac12 \norm{u - u_0}^2 + \lambda TV(u),
  \label{eq:jFunctional}
\end{equation}
where $\norm{\cdot}$ is the $L_2$ norm and all function we consider belong to
the class $BV(\Omega)$, i.\,e. the class of bounded variation on the set
$\Omega$ functions.
%
The expression $\frac12 \norm{n-n_0}^2$ is called a fidelity term and
$\lambda TV(u)$ is called a regularization term and $\lambda$ is regularization
parameter.

@@

\end{comment}

Continuous functions of two variables have a set of topological characteristics
referred to as linear variations. Kronrod\cite{mak2} introduced the notion of a
regular component of the level set of a continuous function of two variables.
The simplest topological characteristic in linear variation theory is the number
of regular components for all level sets of a function. In \cite{mak3,mak4,mak5}
was discussed the necessity of the using a linear variation in the image
restoration theory.

The problem of computing the linear variation in discrete case is equivalent 
to the problem of counting the number of connected components (CC) in a binary
image with 8-connectivity. This is usually done through CC labeling, and many
approaches for that are known\cite{hechao}. We came to the labeling problem
while searching the algorithm for linear variation computing. Of course, the
labeling problem also is well known in the digital image processing theory.

@@

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node[cell] at (0.5, 0.5) {};
    \foreach \x/\y [count=\i from 0] in {0/1,1/1,0/0,1/0} {
      \node[whitebox] at (\x,\y) {\i};
    }
  \end{tikzpicture}
  \caption{Cell pixels enumeration}
  \label{fig:pixelsEnumeration}
\end{figure}

@@

\texten{
Note that this algorithm outputs not the matrix of final labels, but only the
number of CC. This is the place in which it differs from some common two-pass
approaches for CC labeling, as it is an algorithm not for labeling, but just for
counting CC. The latter is exactly what is needed for the aforementioned linear
variation problem.
}\textru{
Отметим, что этот алгоритм выдаёт не матрицу финальных меток, а только
количество компонент связности.
Именно в этом месте он отличается от некоторых известных подходов к CC labeling.
Для текущей задачи нам нужно именно считать компоненты связности.
}

@@

\section{Conclusion}

The problem of linear variation computing can be reduced to the problem of
counting connected components in a binary image with eight-connected
connectivity. This paper presents an efficient way to convert the initial binary
image with 8-connectivity into a condensed (non-binary) image with new
connectivity that is 2 times smaller in each dimension than the initial image.
Most approaches for connected components labeling are still valid for the new
image. As time and memory consumptions of conventional approaches usually depend
linearly on the number of pixels, running them on the condensed image can be up
to 4 times more efficient than running on the initial image. The method is
essentially a modification of some known raster algorithms for labeling that
groups pixels into $2 \times 2$ cells. A performance benchmark of the proposed
method applied to some approaches on noise images is provided. It is shown at
least up to 2 times more quick results could be received.

\section{Acknowledgements}

The work was supported by the Ministry of Education and Science of Russian
Federation (grant 2/1766/2014K).

@@

%\bibitem {mak1}
% Rudin, L., Osher, S., Fatemi, E.:
% Nonlinear total variation based noised removal algorithms.
% Phys. D. 60, 259-268 (1992)

\bibitem {mak2}
Kronrod, A.:
On functions of two variables.
Uspehi Mat. Nauk 5, 1(35), 24-134(1950)
